{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
removed package bussproofs
added rules for multhreaded execution

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{bussproofs}
\usepackage{mathpartir}
\usepackage{nameref}
\usepackage{url}

@@

>>>>

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{mathpartir}
\usepackage{nameref}
\usepackage{url}

@@

\begin{figure}
\begin{align*}
\inferrule{pick(s, h) = ctid \\ s.pc(ctid) = i \\ P[i] \in SeqIns \\
\langle s(ctid), s.gmem\rangle \leadsto_{seq} \sigma,\mu \\ \sigma.pc \neq \mathtt{exit}}
{s,h \leadsto_{conc} s[lst(ctid) := \sigma, gmem := \mu], \langle ctid, se(i)\rangle :: h}
\end{align*}

\begin{align*}
\inferrule{pick(s, h) = ctid \\ s.pc(ctid) = i \\ P[i] \in SeqIns \\
\langle s(ctid), s.gmem\rangle \leadsto_{seq} \sigma,\mu \\ \sigma.pc = \mathtt{exit}}
{s,h \leadsto_{conc} s[lst := lst \\ ctid, gmem := \mu], \langle ctid, se(i)\rangle :: h}
\end{align*}

\begin{align*}
\inferrule{pick(s, h) = ctid \\ s.pc(ctid) = i \\ P[i] = \mathtt{start} pc \\
fresht_{se(i)}(s) = ntid \\ s(ctid).[pc := i + 1] = \sigma'}
{s,h \leadsto_{conc} s.[lst(ctid) := \sigma', lst(ntid) := \lambda_{init}(pc)],
\langle ctid, se(i)\rangle :: h}
\end{align*}
\caption{Multithreaded execution.}
\label{fig:multithreaded-execution}
\end{figure}
